---
title: "BGCGH Evaluation 2023"
author: "Amy Shuff"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
```

``` {r, results='hide'}

library(knitr)
library(usethis)
library(tidyverse)
library(janitor)
library(reshape2)
library(stringr)
library(here)
library(readxl)
library(pdftools)

```

# Evaluation questions

- How are the BGCGH school-based programs implementing the Texas ACE for the 2022-2023 school year impacting children through the focused program areas of: Academic Success, Social-Emotional Development and Attendance?

- How does BGCGH support equitable access to quality after school programming?

- How have BGCGH ACE sites compared to each other over the past 3 years?

- What impact has BGCGH ACE had on children over the past 5 years of programming?

- How has BGCGH ACE supported parents?



```{r}

```

\

# Data

```{r}

# Import all files from working directory (this is everything sent to us by BGCGH)

csv.file.list <- list.files(pattern='*.csv', recursive = TRUE)
csv.list <- sapply(csv.file.list, read.csv, simplify = FALSE)

xlsx.file.list <- list.files(pattern='*.xlsx', recursive = TRUE)
xlsx.list <- sapply(xlsx.file.list, read_xlsx, simplify = FALSE)

pdf.file.list <- list.files(pattern='*.pdf', recursive = TRUE)
pdf.list <- sapply(pdf.file.list, pdf_text, simplify = FALSE)

```

## 2018-2022 ACE Data 

This houses grade and attendance data from 2018-2022 

Questions: 
- Are UID, Member ID, and Club ID all the same thing? Are these identifying individual students?
- What’s the difference between School Day Classes and School Day Classes Passed?
- ACE = Afterschool Centers on Education?



```{r}

# I went in to each ACE file and manually changed column names so that they were all the same. Could have coded it, but I assume they'll give us different things again next year.

# SOM 21st CCLC. Center Name C1. What is this?
# Has GPA instead of subject grade letters like other files
# Also, they shared names here and I don't think they should should have done that. I'll delete those after I figure this file out.
View(csv.list[[1]])

# Look at each file individually to see what it contains and if changes need to be made before it's joined with the others

# ACE Spring 2021
View(csv.list[[2]])
View(csv.list[[3]]) # has extra values in "ACE.Days.Attended"
View(csv.list[[4]])
View(csv.list[[5]])
View(csv.list[[6]]) # includes Year (2021) and Term (Spring). UID had preceding C for some sites. I took those out.

# Join all ACE Spring 2021 files together
# Need to include [[3]] after they send us the fixed file
ace2021 <- bind_rows(list(csv.list[[2]], csv.list[[4]], csv.list[[5]], csv.list[[6]]), .id = "id") %>% 
  mutate(Year = as.numeric(2021),
         Term = "Spring",
         Data = "ACE")


# ACE 2022
# Club.ID now starts with site name initials instead of a column for HostSiteName.
View(csv.list[[7]]) # Grade is number (1)
View(csv.list[[8]]) # Grade is number (1)
View(csv.list[[9]]) # Grade is character (1st), but one is listed as 1nd. Figure out what that should be.
View(csv.list[[10]]) # Grade is character (1st)
View(csv.list[[11]]) # Grade is character (1st)

# Join all 2022 files together
ace2022 <- bind_rows(list(csv.list[[7]], csv.list[[8]]), .id = "id") %>% 
  mutate(Year = as.numeric(2022),
         Data = "ACE",
         Grade = gsub("1", "1st", Grade),
         Grade = gsub("2", "2nd", Grade),
         Grade = gsub("3", "3rd", Grade),
         Grade = gsub("4", "4th", Grade),
         Grade = gsub("5", "5th", Grade),
         Grade = gsub("6", "6th", Grade),
         Grade = gsub("7", "7th", Grade),
         Grade = gsub("8", "8th", Grade)) %>% 
  bind_rows(., list(csv.list[[9]], csv.list[[10]], csv.list[[11]]), .id = "id") %>% 
  mutate(Year = as.numeric(2022),
         Data = "ACE")

    
```


## YPQI Data 

We participate in the annual Youth Program Quality Intervention provided by United Way to conduct a self-assessment on 4 key areas: Safe Environment, Supportive Environment, Interaction, and Engagement. The data provided is a comprehensive breakdown by Club of how they were assessed in the 4 key areas which are further broken down into deeper domains.  

Please note, The Women’s Home, Westwood, and Woodview did not participate in the YOPQI process in 2020 nor 2021 due to the pandemic so I have included their 2019 report instead. 

```{r}

pdf.file.list
pdf.list

```

## NYOI Data 

We participate in an annual survey to hear directly from youth about their Club experience. This survey collects information on selected modules that vary Club. Some of the modules include: Club Experience, Safety, Healthy Lifestyles, Academic Success, Good Character, SEL, Art, STEM, Bullying, Workforce, Risky Behavior. , 

```{r}

xlsx.file.list
xlsx.list


```

## Member Demographics 

This is a report pulling demographic statistics for each Club. 

```{r}

```

```{r}

Import PDF data


###### Provider clean #######
url<- c("https://www.twc.texas.gov/files/twc/commission_meeting_materials_09.13.22_item16_bcy23_cc_targets.pdf")
raw_text <- map(url, pdf_text)

clean_table1<-function(raw) {
  #split the single pages 
  raw <-map(raw, ~ str_split(.x, "\\n") %>% unlist())
  #concatente the split pages
  raw <- reduce(raw, c)
  
  #specify the start and end of the table data
  table_start <- stringr::str_which(tolower(raw),"Board Name")
  table_end <- stringr::str_which(tolower(raw), "Sum of Boards")
  table_end <- table_end[min(which(table_end >table_start))]
  
  #Build the table and remove special characters
  table <- raw[(table_start):(table_end)]
  table <- str_replace_all(table,"\\s{2,}", "|")
  text_con <- textConnection(table)
  data_table <- read.csv(text_con, sep = "|")

#Create a list of column names
colnames(data_table)<- c("Board Name","#","CY23 Base Allocation","4% Quality Allocation", "Amount Available to Operate the Subsidized CC Program", "Presumed Semi-Fixed Admin/Ops Set Aside","Supplemental Distribution","Available for Direct Care (DC) & Variable Admin/Ops","Variable
Admin/Ops per Unit","Estimated Avg Provider Reimbursement Rate", "Presumed PSOC","System Cost Per Unit", "BCY23 Target")
data_table
}

results <- map_df(raw_text, clean_table1) #I am stuck here and I don't know why-CT (see Amy's attempt below)



# Amy's attempt:

raw_text <- pdf_text("https://www.twc.texas.gov/files/twc/commission_meeting_materials_09.13.22_item16_bcy23_cc_targets.pdf") 

raw_table <- map(raw_text[3], ~ str_split(.x, "\\n") %>% unlist())

#specify the start and end of the table data
table_start <- raw_table[[1]] %>% 
    str_which("Board Name")
table_end <- raw_table[[1]] %>% 
    str_which("Sum of Boards")

#Build the table and remove special characters
table <- raw_table[[1]][(table_start):(table_end)]
table <- str_replace_all(table,"\\s{2,}", "|")
text_con <- textConnection(table)
data_table <- read.csv(text_con, sep = "|")
  
#Create a list of column names
colnames(data_table)<- c("Board Name","#","CY23 Base Allocation","4% Quality Allocation", "Amount Available to Operate the Subsidized CC Program", "Presumed Semi-Fixed Admin/Ops Set Aside","Supplemental Distribution","Available for Direct Care (DC) & Variable Admin/Ops","Variable
Admin/Ops per Unit","Estimated Avg Provider Reimbursement Rate", "Presumed PSOC","System Cost Per Unit", "BCY23 Target")


```
