---
title: "BGCGH Evaluation 2023"
author: "Amy Shuff"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
```

Last year's report was Fall 2021 - Spring 2022. 
This year's report will be Fall 2022 - Spring 2023.


By next check-in:

- check with district about lack of report cards

- New SOM 2021 Spring Upload file: Folder “2018 - 2022 ACE Data”, file name “Copy of SOM 2021 Spring Upload”


To expect with the next data upload this summer:

- Attendance numbers. (In previous years the total attendance has been: 1622, 1227, and 1504.)

- Fall 2023 ACE files (report cards) - will probably only get a few hundred again


# Next Questions

- You said the 2021 data we have is from the fall. We have the same number of report cards, from the same grades and the same sites, other than woodview, as the spring 2021 data in last year's report. Quite the coincidence if it isn't the exact same data.

- 2021 ACE data is only from Spring. Should we also have Fall?

- The ACE folder is named 2018-2022. Are we supposed to grab 2018-2020 data from the old evaluation reports? We can't do this because most of the graphs do not have individual data labels. Also, the exact same graphs were not recreated each year. We could give very basic comparisons like total attendance once we have those numbers for 2023.

- 2019 report is not final 

- Quite a few grades missing from 2021 data.


``` {r, results='hide'}

library(knitr)
library(usethis)
library(tidyverse)
library(janitor)
library(reshape2)
library(stringr)
library(here)
library(readxl)
library(pdftools)

```


# Data

```{r}

# Import all files from working directory (this is everything sent to us by BGCGH)


# Import all cvs files
csv.file.list <- list.files(pattern='*.csv', recursive = TRUE)
csv.list <- sapply(csv.file.list, read.csv, simplify = FALSE, USE.NAMES = TRUE)


# Import all xlsx files. These have a tab for each site, so I'll use a loop to read in all the tabs.
xlsx.file.list <- list.files(pattern='*.xlsx', recursive = TRUE)
xlsx.list <- list()
for (file in xlsx.file.list){xlsx.list[[file]] <- sapply(excel_sheets(file), read_xlsx, path = file, simplify = FALSE, USE.NAMES = TRUE)}


# Import all pdf files
pdf.file.list <- list.files(pattern='*.pdf', recursive = TRUE)
pdf.list <- sapply(pdf.file.list, pdf_text, simplify = FALSE, USE.NAMES = TRUE)

```

## ACE Data 

This houses grade and attendance data from 2018-2022.

Texas Afterschool Centers on Education (Texas ACE™) program. Grant funding to provide high-quality academic enrichment opportunities for children and youth during non-school hours.

Messaging guide: https://tea.texas.gov/sites/default/files/texas_ace_messaging_guide2021_22.pdf.pdf

The school district supplies the report cards

Notes from last year's report:

A limitation of this analysis is the amount of available report cards. Despite the number of Club Members in Texas ACE™, only a sample size of 351 report cards were available. Because of the variability in grade level and Club site within the sample, this data has limited generalizability of the actual grade distribution within the five Clubs.

Number of report cards do not match total Membership numbers. Analysis is limited to the total number of report cards provided N=351

(Looking at their report card numbers, we have that same data again this year.)

Folder for last year's report: https://childrenatrisk.sharepoint.com/sites/GDrive/Shared%20Documents/Forms/AllItems.aspx?ct=1683734745868&or=Teams%2DHL&ga=1&id=%2Fsites%2FGDrive%2FShared%20Documents%2FCenter%20for%20Social%20Measurement%20and%20Evaluation%2FSharmily%20Working%2FBoys%20ang%20Girls%20Club%20Info%2FData%20Sets&viewid=31449e19%2Dda16%2D4372%2D8e07%2D45d6b35480c4


Notes from 19-20 report:

number of days of BGCGH Texas ACE programming
attended by a given student could not be calculated to a reasonable level of certainity because of disparities
in data collection and management procedures.

Required Funding Statement: Funded by the 21st CCLC Program administered by the US Department of
Education


```{r}

# ACE Data

# Evaluation question: What impact has BGCGH ACE had on children over the past 5 years of programming?


# I went in to each ACE file and manually changed column names in Excel so that they were all the same. Could have coded it, but I assume they'll give us different things again next year.

# Look at each file individually to see what it contains and if changes need to be made before it's joined with the others.

# ACE Spring 2021
# View(csv.list[[5]]) # includes Year (2021) and Term (Spring). UID had preceding C for some sites. I took those out.

# Join all ACE Spring 2021 files together

ace2021 <- bind_rows(list(csv.list[[1]], csv.list [[2]], csv.list[[3]], csv.list[[4]], csv.list[[5]]), .id = "id") %>% 
  mutate(Year = as.numeric(2021),
         Term = "Spring",
         Data = "ACE",
         HostSiteName = gsub("The Womens' Home", "The Womans' Home", HostSiteName)) %>% 
  rename(Site = HostSiteName,
         Number.of.School.Days = SchoolDaysEnrolled,
         Number.of.Texas.ACE.Days = ACE.Days.Attended,
         Math = MathGrade,
         English.Reading = ReadingGrade) 

# figure out how to remove duplicate UIDs
ace2021.duplicates <- ace2021$UID[duplicated(ace2021$UID)]
# paste(ace2021.duplicates)
# "1841070" "1837954" "1838312" "1838401" "1839453" "1840898"

ace2021 <- ace2021 %>% 
  select(Site, Grade, Number.of.School.Days, Number.of.Texas.ACE.Days, Math, English.Reading, Year, Term, Data)


# ACE 2022 - Fall
# Club.ID now starts with site name initials instead of a column for HostSiteName.
# View(csv.list[[6]]) # Grade is number (1)
# View(csv.list[[7]]) # Grade is number (1)
# View(csv.list[[8]]) # Grade is character (1st), but one is listed as 1nd. Changed to 1st.
# View(csv.list[[9]]) # Grade is character (1st)
# View(csv.list[[10]]) # Grade is character (1st)

# Join all 2022 files together
ace2022 <- bind_rows(list(csv.list[[6]], csv.list[[7]]), .id = "id") %>% 
  mutate(Data = "ACE",
         Grade = gsub("1", "1st", Grade),
         Grade = gsub("2", "2nd", Grade),
         Grade = gsub("3", "3rd", Grade),
         Grade = gsub("4", "4th", Grade),
         Grade = gsub("5", "5th", Grade),
         Grade = gsub("6", "6th", Grade),
         Grade = gsub("7", "7th", Grade),
         Grade = gsub("8", "8th", Grade)) %>% 
  bind_rows(., list(csv.list[[8]], csv.list[[9]], csv.list[[10]]), .id = "id") %>% 
  mutate(Year = as.numeric(2022),
         Data = "ACE")
ace2022 <- ace2022 %>% 
  mutate(Site = ifelse(substr(ace2022$Club.ID, 1, 3) == "SOM", "Spring Oaks Middle", ""),
         Site = ifelse(substr(ace2022$Club.ID, 1, 3) == "SBE", "Spring Branch Elementary", Site),
         Site = ifelse(substr(ace2022$Club.ID, 1, 3) == "TWH", "The Womans' Home", Site),
         Site = ifelse(substr(ace2022$Club.ID, 1, 3) == "WWE", "Westwood Elementary", Site),
         Site = ifelse(substr(ace2022$Club.ID, 1, 2) == "WV", "Woodview Elementary", Site),
         Term = "Fall")

ace2022.duplicates <- ace2022$Club.ID[duplicated(ace2022$Club.ID)]
# paste(ace2022.duplicates)
# No duplicates in 2022 data

ace2022 <- ace2022 %>% 
  select(Site, Grade, Number.of.School.Days, Number.of.Texas.ACE.Days, Math, English.Reading, Year, Term, Data)

# - 2022 Fall ACE data has 174 school days for all students. 2021 ACE data has SchoolDaysEnrolled and SchoolDayClasses, which both range from 0 to 94. But they're not always the same, nor do they match ACE Days Attended.
```


BGCGH told us this 2022 data was from the fall, but it looks exactly like last year's data except for Woodview.

```{r}

ace2022.counts <- ace2022 %>% 
  group_by(Site) %>% 
  summarise(Kindergarten = sum(Grade == 'Kinder'),
            "1st" = sum(Grade == '1st'),
            "2nd" = sum(Grade == '2nd'),
            "3rd" = sum(Grade == '3rd'),
            "4th" = sum(Grade == '4th'),
            "5th" = sum(Grade == '5th'),
            "6th" = sum(Grade == '6th'),
            "7th" = sum(Grade == '7th'),
            "8th" = sum(Grade == '8th'))
  
kable(ace2022.counts, caption = "2022 Report Card Counts")

```










```{r}
# Evaluation Question: How have BGCGH ACE sites compared to each other over the past 3 years?

ace <- bind_rows(ace2021, ace2022) %>%
  # Kinder has Pass/Fail. They were excluded from previous reports.
  filter(!Grade == "Kindergarten" & !Grade == "Kinder") %>% 
  # 2022 GPA Methodology – Letter grades were converted to gpa scale where A=4, B=3, C=2, D=1, F=0 then averaged and rounded to the nearest whole number. Methodology consistent with 2020-2021 report  
  mutate(Math = ifelse(Math == "A", 4, Math),
         Math = ifelse(Math == "B", 3, Math),
         Math = ifelse(Math == "C", 2, Math),
         Math = ifelse(Math == "D", 1, Math),
         Math = ifelse(Math == "F", 0, Math),
         Math = as.numeric(Math),
         English.Reading = ifelse(English.Reading == "A", 4, English.Reading),
         English.Reading = ifelse(English.Reading == "B", 3, English.Reading),
         English.Reading = ifelse(English.Reading == "C", 2, English.Reading),
         English.Reading = ifelse(English.Reading == "D", 1, English.Reading),
         English.Reading = ifelse(English.Reading == "F", 0, English.Reading),
         English.Reading = as.numeric(English.Reading)) 

# One kid has an S in math, but as.numeric makes it NA, so it's automatically dropped
# Quite a few grades missing from 2021 data

# We should expect 2023 Spring ACE Data?

```



```{r}

# Average Math and English/Reading GPAs

ace.averages <- ace %>% 
  group_by(Site, Year, Term) %>% 
  summarise(Math = mean(Math, na.rm = TRUE),
            English.Reading = mean(English.Reading, na.rm = TRUE),
            "Number of Report Cards" = n()) %>% 
  mutate_if(is.numeric, round, digits = 2)

kable(ace.averages, caption = "Average GPA by Site and Year", digits = 2)

# one of the old reports did a histogram with the frequency of grades. I like that idea.
# geom_histogram() or geom_freqpoly()

```


### Math GPA

On average, math grades seem to have improved from 2021 to 2022. But we also have significantly fewer report cards to analyze, so there's a chance this wasn't a significant change.

```{r}

# Math GPA by Site and Year

ggplot(ace.averages, aes(x = Site, y = Math, fill = factor(ace.averages$Year))) +
  geom_bar(stat = "identity", position = "dodge") +
  coord_flip() +
  geom_text(aes(label = Math), 
                color = "white",
            position = position_dodge(width = .9),
            hjust = 2) +
  labs(title = "Average Math GPA by Site and Year") +
  theme(panel.background = element_blank()) +
  ylab("Average Math GPA") +
  xlab("") +
  guides(fill = guide_legend(title = "Year")) +
    scale_fill_hue(l=40)

    
```


### English/Reading GPA

As with Math, there seems to be an increase in the average English/Reading grades from 2021 to 2022.

```{r}

# English/Reading GPA by Site and Year

ggplot(ace.averages, aes(x = Site, y = English.Reading, fill = factor(ace.averages$Year))) +
  geom_bar(stat = "identity", position = "dodge") +
  coord_flip() +
  geom_text(aes(label = English.Reading), 
                color = "white",
            position = position_dodge(width = .9),
            hjust = 2) +
  labs(title = "Average English/Reading GPA by Site and Year") +
  theme(panel.background = element_blank()) +
  ylab("Average English/Reading GPA") +
  xlab("") +
  guides(fill = guide_legend(title = "Year")) +
    scale_fill_hue(l=40)


    
```

### Overall Grades

2019 report has average GPA by site and subject. We would have to weight the averages by attendance for that year to get total subject average. There isn't a report card for each student, so this wouldn't be exact.

2020 report has average grade by site and subject as well. (Math: SB=2.41, SOM=2.32, TWH=2.3, WW=2.34, WV=1.74, Reading: SB = 2.29, SOM=2.13, TWH=2.2, WW=2.4, WV=1.75) There are 1,072 report cards and 1,216 members.

2021 has averages by subject and term.. I averaged the two terms and added it to the data below.

It looks like there's a dramatic increase in grades for 2022, but with so few report cards, it's really hard to say if it's a significant increase.


```{r}

ace.overall <- ace %>% 
  group_by(Year) %>% 
  summarise(Math = mean(Math, na.rm = TRUE),
            English.Reading = mean(English.Reading, na.rm = TRUE),
            "Number of Report Cards" = n()) %>% 
  rbind(., c(2020, 2.25, 2.1, 1432)) %>% 
  rbind(., c(2019, (2.41*172+2.32*419+2.3*144+2.34*250+1.74*231)/1216, (2.29*172+2.13*419+2.2*144+2.4*250+1.75*231)/1216, 1072)) %>% 
  mutate_if(is.numeric, round, digits = 2) %>% 
  arrange(Year)

kable(ace.overall, caption = "Average GPA by Year", digits = 2)

ace.overall.plot <- ace.overall %>% 
  pivot_longer(c(Math, English.Reading), 
               names_to = "Subject", 
               values_to = "GPA")

ggplot(ace.overall.plot, aes(x = Year)) +
  geom_line(aes(y = GPA, color = Subject)) +
  coord_cartesian(ylim = c(0, 4)) +
  labs(title = "GPA Averages by Year",
       subtitle = "for all BGCGH sites combined") +
  scale_x_continuous(breaks=seq(2019, 2022, 1))



```



## YPQI Data 

We participate in the annual Youth Program Quality Intervention provided by United Way to conduct a self-assessment on 4 key areas: Safe Environment, Supportive Environment, Interaction, and Engagement. The data provided is a comprehensive breakdown by Club of how they were assessed in the 4 key areas which are further broken down into deeper domains.  

Please note, The Women’s Home, Westwood, and Woodview did not participate in the YOPQI process in 2020 nor 2021 due to the pandemic so I have included their 2019 report instead. 



```{r}

# pdf.file.list
# pdf.list

# Everything we have right now is from 2022.

```

## NYOI Data 

Boys & Girls Clubs of America’s National Youth Outcomes Initiative

Member Survey Report

We participate in an annual survey to hear directly from youth about their Club experience. This survey collects information on selected modules that vary Club. Some of the modules include: Club Experience, Safety, Healthy Lifestyles, Academic Success, Good Character, SEL, Art, STEM, Bullying, Workforce, Risky Behavior. , 

For more information about NYOI and how it measures Boys and Girls Club experiences: https://clubexperience.blog/2018/02/22/how-do-we-measure-the-club-experience/

```{r eval=FALSE, include=FALSE}

# Member Survey Reports
View(xlsx.list[[2]]) #2021
View(xlsx.list[[3]]) #2022, one of the tabs has wonky data

# skip = 8?
# pivot_longer()

nyoi.2021 <- bind_rows(xlsx.list[[2]], .id = "Site") 
# all the detail report columns need to be merged into one


nyoi.2022 <- bind_rows(xlsx.list[[3]], .id = "Site") 


```

## Member Demographics 2023

This is a report pulling demographic statistics for each Club. Percents do not add up to 100 because each site had some percent not reported.

```{r}

# 2023 Club Demographics
# View(xlsx.list[[1]])

club.demographics.2023 <- bind_rows(xlsx.list[[1]], .id = "Site") %>% 
  rename(Demographic = Gender,
         demographic.pct = ...2) %>% 
  na.omit() %>% 
  mutate(Site = gsub("SBE", "Spring Branch Elementary", Site),
         Site = gsub("SO", "Spring Oaks Middle", Site),
         Site = gsub("TWH", "The Womans' Home", Site),
         Site = gsub("WV", "Woodview Elementary", Site),
         Site = gsub("WW", "Westwood Elementary", Site))

# Gender: Male, Female
# Race: Asian, Black, Latino, Native, White, 2+
# Age: 5 to 9, 10 to 12, 13 to 18


```

### Gender

Westwood Elementary had the highest not reporting gender, at 11%. Note that the options for this survey were only Male or Female.

```{r}

# Gender: Male, Female

gender <- club.demographics.2023 %>% 
  filter(Demographic == 'Male' | Demographic == 'Female') %>% 
  mutate(Male = ifelse(Demographic == 'Male', demographic.pct, NA),
        Female = ifelse(Demographic == "Female", demographic.pct, NA)) %>% 
  group_by(Site) %>% 
  summarise(Male = sum(Male, na.rm = T),
            Female = sum(Female, na.rm = T)) %>% 
  mutate("Not Set" = 1-Male-Female)

kable(gender, lables = scales::label_percent())

gender.plot <- club.demographics.2023 %>% 
 filter(Demographic == 'Male' | Demographic == 'Female')  

ggplot(gender.plot, aes(x = Site, y = demographic.pct)) +
  geom_col(aes(fill = Demographic)) +
  coord_flip() +
  geom_text(aes(label = scales::percent(demographic.pct)), color = "white", hjust = 1.5, position = "stack") +
  labs(title = "Gender") +
  theme(panel.background = element_blank(),
        axis.text.x = element_blank(),
        axis.ticks.x = element_blank()) +
  ylab("Percent") +
  xlab("") +
    scale_fill_hue(l=40)

```

### Race

Latino made up the highest percent of student race at any site, although lack of response was high at Spring Branch Elementary (76%), Spring Oaks Middle (62%) and The Womans’ Home (49%).

```{r}

# Race: Asian, Black, Latino, Native, White, 2+

race <- club.demographics.2023 %>% 
  filter(Demographic == 'Latino' | 
           Demographic == 'White'| 
           Demographic == 'Black'| 
           Demographic == 'Asian' | 
           Demographic == 'Native'| 
           Demographic == '2+') %>% 
  mutate(
      Latino = ifelse(Demographic == "Latino", demographic.pct, NA),
      White = ifelse(Demographic == "White", demographic.pct, NA),
      Black = ifelse(Demographic == "Black", demographic.pct, NA),
      Asian = ifelse(Demographic == "Asian", demographic.pct, NA),
      Native = ifelse(Demographic == "Native", demographic.pct, NA),
      Multiple = ifelse(Demographic == "2+", demographic.pct, NA)) %>% 
  group_by(Site) %>% 
  summarise(
            Latino = sum(Latino, na.rm = T),    
            White = sum(White, na.rm = T),       
            Black = sum(Black, na.rm = T),
            Asian = sum(Asian, na.rm = T),
            Native = sum(Native, na.rm = T),
            Multiple = sum(Multiple, na.rm = T)) %>% 
  mutate("Not Set" = 1-Asian-Black-Latino-Native-White-Multiple)

kable(race)

race.plot <- 
  club.demographics.2023 %>% 
  filter(Demographic == 'Latino' | 
           Demographic == 'White'| 
           Demographic == 'Black'| 
           Demographic == 'Asian' | 
           Demographic == 'Native'| 
           Demographic == '2+') %>% 
    mutate(Demographic = factor(Demographic, levels=c("2+", "Asian", "Native", "Black", "White", "Latino")))


ggplot(race.plot, aes(x = Site, y = demographic.pct)) +
  geom_col(aes(fill = Demographic)) +
  coord_flip() +
  geom_text(aes(label = ifelse(Demographic == "Latino", scales::percent(demographic.pct), '')), 
                color = "white", hjust = 2, position = "stack") +
  labs(title = "Race") +
  theme(panel.background = element_blank(),
        axis.text.x = element_blank(),
        axis.ticks.x = element_blank()) +
  ylab("Percent") +
  xlab("")  +
    scale_fill_hue(l=40)

# The colors of this graph are not great

```

### Age

Ages five to nine were the most represented at all sites except Spring Oaks Middle, which was primarily ages thirteen to eighteen.

```{r}

# Age: 5 to 9, 10 to 12, 13 to 18

age <- club.demographics.2023 %>%
  filter(Demographic == '5 to 9' | 
           Demographic == '10 to 12'| 
           Demographic == '13 to 18') %>% 
  mutate(
      "Five_Nine" = ifelse(Demographic == '5 to 9', demographic.pct, NA),
      "Ten_Twelve" = ifelse(Demographic == '10 to 12', demographic.pct, NA),
      "Thirteen_Eighteen" = ifelse(Demographic == '13 to 18', demographic.pct, NA)) %>% 
  group_by(Site) %>% 
  summarise(Five_Nine = sum(Five_Nine, na.rm = T),    
            Ten_Twelve = sum(Ten_Twelve, na.rm = T),       
            Thirteen_Eighteen = sum(Thirteen_Eighteen, na.rm = T)) %>% 
  mutate("Not Set" = 1-Five_Nine-Ten_Twelve-Thirteen_Eighteen)

# might try using pivot_wider() on club.demographics.2023 to see if it works better

kable(age)

age.plot <- 
  club.demographics.2023  %>% 
  filter(Demographic == '5 to 9' | 
           Demographic == '10 to 12'| 
           Demographic == '13 to 18') %>% 
  mutate(Demographic = factor(Demographic, levels=c("13 to 18", "10 to 12", "5 to 9")))


ggplot(age.plot, aes(x = forcats::fct_rev(Site), y = demographic.pct)) +
  geom_col(aes(fill = Demographic)) +
  coord_flip() +
  geom_text(aes(label = ifelse(Demographic == "5 to 9" | Demographic == "13 to 18", scales::percent(demographic.pct), '')), 
                color = "white", hjust = 1.5) +
  labs(title = "Age") +
  theme(panel.background = element_blank(),
        axis.text.x = element_blank(),
        axis.ticks.x = element_blank()) +
  ylab("Percent") +
  xlab("")  +
    scale_fill_hue(l=40)


```


```{r eval=FALSE, include=FALSE}

# Copy and pasted example code of extracting tables from a pdf (From Child Care project)

###### Provider clean #######
url<- c("https://www.twc.texas.gov/files/twc/commission_meeting_materials_09.13.22_item16_bcy23_cc_targets.pdf")
raw_text <- map(url, pdf_text)

clean_table1<-function(raw) {
  #split the single pages 
  raw <-map(raw, ~ str_split(.x, "\\n") %>% unlist())
  #concatente the split pages
  raw <- reduce(raw, c)
  
  #specify the start and end of the table data
  table_start <- stringr::str_which(tolower(raw),"Board Name")
  table_end <- stringr::str_which(tolower(raw), "Sum of Boards")
  table_end <- table_end[min(which(table_end >table_start))]
  
  #Build the table and remove special characters
  table <- raw[(table_start):(table_end)]
  table <- str_replace_all(table,"\\s{2,}", "|")
  text_con <- textConnection(table)
  data_table <- read.csv(text_con, sep = "|")

#Create a list of column names
colnames(data_table)<- c("Board Name","#","CY23 Base Allocation","4% Quality Allocation", "Amount Available to Operate the Subsidized CC Program", "Presumed Semi-Fixed Admin/Ops Set Aside","Supplemental Distribution","Available for Direct Care (DC) & Variable Admin/Ops","Variable
Admin/Ops per Unit","Estimated Avg Provider Reimbursement Rate", "Presumed PSOC","System Cost Per Unit", "BCY23 Target")
data_table
}

results <- map_df(raw_text, clean_table1) #I am stuck here and I don't know why-CT (see Amy's attempt below)



# Amy's attempt:

raw_text <- pdf_text("https://www.twc.texas.gov/files/twc/commission_meeting_materials_09.13.22_item16_bcy23_cc_targets.pdf") 

raw_table <- map(raw_text[3], ~ str_split(.x, "\\n") %>% unlist())

#specify the start and end of the table data
table_start <- raw_table[[1]] %>% 
    str_which("Board Name")
table_end <- raw_table[[1]] %>% 
    str_which("Sum of Boards")

#Build the table and remove special characters
table <- raw_table[[1]][(table_start):(table_end)]
table <- str_replace_all(table,"\\s{2,}", "|")
text_con <- textConnection(table)
data_table <- read.csv(text_con, sep = "|")
  
#Create a list of column names
colnames(data_table)<- c("Board Name","#","CY23 Base Allocation","4% Quality Allocation", "Amount Available to Operate the Subsidized CC Program", "Presumed Semi-Fixed Admin/Ops Set Aside","Supplemental Distribution","Available for Direct Care (DC) & Variable Admin/Ops","Variable
Admin/Ops per Unit","Estimated Avg Provider Reimbursement Rate", "Presumed PSOC","System Cost Per Unit", "BCY23 Target")


```


# Evaluation questions

- How are the BGCGH school-based programs implementing the Texas ACE for the 2022-2023 school year impacting children through the focused program areas of: Academic Success, Social-Emotional Development and Attendance?

- How does BGCGH support equitable access to quality after school programming?

- How have BGCGH ACE sites compared to each other over the past 3 years?

- What impact has BGCGH ACE had on children over the past 5 years of programming?

- How has BGCGH ACE supported parents?

```{r}

```



# Outlines from past years

21-22 (18 pages), CHILDREN AT RISK
(Did not include interviews, although 20-21 and 19-20 both did)
Acknowledgements 
Executive Summary 
Introduction and Background
Descriptive Statistics on Club Members
    Members and Attendance
    Academic Distribution Summary
Club-Level Data
    National Youth Outcome Initiative – Club Member Experience
Results and Implications
    Attendance
    Academic Performance
    Member Experience
Research Limitations
Conclusions and Recommendations
Appendix One: Additional Club Level Data

20-21 (33 pages), Meadows Mental Hleath Policy Institute
Executive Summary
Introduction and Background
Descriptive Statistics on Club Members
    Members and Attendance
    Members by School Grade Level
Club-Level Data
Staff Interview Findings
    Strengths
    Challenges
Results and Implications
    Major Findings
Research Limitations
Conclusions and Recommendations
Appendix One: Member-Level Data Cleaning Notes
Appendix Two: Additional Member-Level Details
Appendix Three: Additional Club-Level Details


19-20 (34 pages), Patrick S. Tennant, Ph.D., LMFT
Executive Summary
Introduction
Descriptive Statistics of BGCGH Club Members
    Number of Members
    Member Demographic Details
    BGCGH Texas ACETM Program Days Attended
    Academic Grades, Attendance, and Referrals
Analyses Based on Regular Attendance (also done in the 18-19 report, but not after)
    Defining Regular Attendance
    Academic Grades by Regular Attendance
    School Days Absent by Regular Attendance
    Referrals by Regular Attendance
Club-level Data
    National Youth Outcomes Initiative
    Youth Program Quality Assessment
Coronavirus Pandemic
    Timeline and Services
    Interviews
Results and Implications
    Findings
    Limitations
    Conclusions and Recommendations
Appendices 
    Appendix A: Member-level Data Cleaning Notes
    Appendix B: Additional Member-level Details
    Appendix C: Additional Club-level Details
    
18-19 (15 pages), Patrick S. Tennant, Ph.D., LMFT

(Did not include interviews)


# Data Cleaning Notes

One kid has an S in math, but as.numeric makes it NA, so it's automatically dropped

2021 ACE data has 6 duplicate member ids:
"1841070" "1837954" "1838312" "1838401" "1839453" "1840898"
